Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-11 inst/examples/20160715-slides-Krakow.Rmd
a
s

Overcoming a national gaze in the analysis by focusing on how knowledge production happened through a more complex network of cities.

@@

### Data (1470-1828):

@@

### Publishing activity in Swedish University Towns (Kungliga)

```{r map1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5}
library(dplyr)
library(ggmap)
library(ggplot2)
library(gisfin)
source("funcs.R")
theme_set(get_theme_map())
mapdata <- filter(df0,
          (catalog == "Kungliga" &
	      publication_place %in% c("Stockholm", "Uppsala",
	                         "Greifwald", "Lund", "Tartu"))|
	  (catalog == "Fennica" &
	      publication_place == "Turku")) %>%
      group_by(publication_decade, publication_place,
	       latitude, longitude) %>%
      summarise(n = n())

@@

library(gridExtra)
grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], nrow = 1)
```

@@

### Comparing publishing activity in Swedish University towns

Turku / Uppsala / Lund / Stockholm

```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=6, fig.height=5, fig.show="hold", out.width="170px"}
v <- seq(1500, 1800, 50)
selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
               summarise(n = n()) %>%
	       filter(publication_place %in% selected.places) 
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
df2$publication_place = droplevels(factor(df2$publication_place))
df3 = as.data.frame(spread(df2, publication_decade, n, fill = 0))
df2 = melt(df3)
colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
df2$publication_decade = as.numeric(as.character(df2$publication_decade))
df2$n = as.numeric(as.character(df2$n))
for (catal in unique(df2$catalog)) {
  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
     geom_line(aes(linetype = publication_place)) +
     geom_point(aes(shape = publication_place), size = 3) +
     ylab("Title count (n)") + xlab("Publication year") +  
     ggtitle(catal) +
     scale_x_continuous(breaks = v, labels = v)     
  print(p)

@@

### Rock Bottom of the Great Northern War (1700-1721)

Publisher title count changes around 1700 with a nearly detrimental drop in Turku, significant publishing place in Finland at the time.

```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/drop1700B-1.png

catalogue <- "Fennica"
place <- "Turku"

df <- df0
df <- df %>%
        filter(catalog == catalogue & publication_place == place) %>%
        filter(publication_year >= 1650 & publication_year < 1750)

# Selected ones
top <- names(top(df, "publisher", 5))
df$publisher[!df$publisher %in% top] <- "Other"
df$publisher <- factor(df$publisher, levels = c(top, "Other"))

# Publishing per year & publisher	
npub <- df %>%
     	  group_by(publication_year, publisher) %>%
	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n())

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_year, y = n, group = publisher)) +
       geom_point(size = 5, aes(shape = publisher, color = publisher)) +
       geom_smooth(col = "black", aes(shape = publisher, fill = publisher, color = publisher)) + 
       xlab("Publication year") +
       ylab("Title count (n)") +
       ylim(c(0, 1.1*max(npub$n))) +
       ggtitle(paste("Title count (", place, "/", catalogue, ")", sep = ""))
print(p)
```

@@

### Combining devotional literature and temporary sermons

```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat","hautajaiset","häät","juhlamenot")
catalogue <- "Fennica"
  df <- df0 # selected time span
  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)

  # Selected catalogue with selected topics
  df <- df %>% filter(catalog == catalogue & hit)

  # Selected catalogue with selected years
  df = filter(df0, catalog == catalogue & publication_year >= 1640 & publication_year <= 1828)

  lang <- paste("language.", langs, sep = "")
  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
  dfl <- NULL
  for (lan in lang) {
    # Classify a document to the specifed language
    # If document is assigned with languages, each case is considered
    # so one doc may have multiple entries corresponding to different languages
    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
    # Combine data frames for specified languages
    dflsub <- filter(df, df[[lan]])
    if (nrow(dflsub) > 0) {
      dflsub$language <- gsub("language.", "", lan)
      dfl <- bind_rows(dfl, dflsub)
    }
}

  # -------------------------------------------

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       #geom_point(aes(col = language, shape = language), size = 5) +
       #geom_line(aes(col = language, shape = language)) +
       geom_bar(stat = "identity", aes(fill = language, )) +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
  print(p)
```

>>>>

**Overcoming a national gaze** by focusing on how knowledge production happened through a more complex network of cities.

@@

### Data (1640-1828):

@@

### Turku as a Swedish University Town among Uppsala, Tartu and Stockholm (+ Greifswald and Lund)

```{r map1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5}
library(dplyr)
library(ggmap)
library(ggplot2)
library(gisfin)
source("funcs.R")
theme_set(get_theme_map())
mapdata <- filter(df0,
          (catalog == "Kungliga" &
	      publication_place %in% c("Stockholm", "Uppsala",
	                         "Greifswald", "Lund", "Tartu"))|
	  (catalog == "Fennica" &
	      publication_place == "Turku")) %>%
      group_by(publication_decade, publication_place,
	       latitude, longitude) %>%
      summarise(n = n())

@@

#library(gridExtra)
#grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], nrow = 1)
library(gridExtra)
grid.arrange(pics[[1]], nrow = 1)
```

@@

### Comparing publishing activity in Stockholm and Turku

```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=6, fig.height=5, fig.show="hold", out.width="170px"}
v <- seq(1500, 1800, 50)
selected.places = c("Turku", "Stockholm")
df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
               summarise(n = n()) %>%
	       filter(publication_place %in% selected.places) 
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
df2$publication_place = droplevels(factor(df2$publication_place))
df3 = as.data.frame(spread(df2, publication_decade, n, fill = 0))
df2 = melt(df3)
colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
df2$publication_decade = as.numeric(as.character(df2$publication_decade))
df2$n = as.numeric(as.character(df2$n))
for (catal in unique(df2$catalog)) {
  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
     geom_line(aes(linetype = publication_place)) +
     geom_point(aes(shape = publication_place), size = 3) +
     ylab("Title count (n)") + xlab("Publication year") +  
     ggtitle(catal) +
     scale_x_continuous(breaks = v, labels = v)     
  print(p)

@@

@@
